Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2021-11-01 Presentations/ThirdYearPaperpres.tex
Updates from Overleaf

        \column{0.4\textwidth}
        \centering
        \color{gray}
        \underline{ EHR $\rightarrow$ Healthcare }
        \vspace{-1mm}
        \begin{itemize}
        \color{gray}
            \item Small improvements for severe health conditions \\ \vspace{1mm}
            \tiny(Agha 2014, JHE; McCullough et al 2016, RAND)

@@

            \item Productivity and opinion about EHRs varies drastically \\ \vspace{1mm}
            \tiny (Hitt $\&$ Tambe 2016, ILRR; Butler $\&$ Johnson 2016, IJHEM; Meyerhoefer et al 2016, ILRR)

        \end{itemize}

@@

\begin{frame}{Dep. Variable: Patients Billed with Hospitals}
\begin{figure}[ht]
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_fullsample.pdf}
            \caption{\small All Physicians\\}
        \end{minipage}
        \hspace{0.2cm}
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_oldsample.pdf}
            \caption{\small Phys. $>$ 35 yrs Experience}
        \end{minipage}
    \end{figure}
\end{frame}

@@

\begin{frame}{Plans}
    \begin{itemize}
        \item Analysis on retirement decision of physicians: requires a better understanding of why physicians would drop out of this Medicare data
        \item Investigate other estimation strategies
    \end{itemize}
\end{frame}

>>>>

        \column{0.4\textwidth}
        \centering

        \pause

        \color{blue}
        \underline{ Contribution }
        \vspace{1mm}

        \color{blue}
        Speaks to this question in a particular setting 
            \begin{itemize}
            \color{blue}
                \item Important because health care spending is extremely high
                \item Important to think about physician labor markets because of shortages and access to care issues
            \end{itemize}

\end{columns}
\end{frame}

\begin{frame}{Literature}
\small
\begin{columns}
\setlength{\tabcolsep}{-5pt}
        \column{0.4\textwidth}
        \centering
        \underline{ EHR $\rightarrow$ Healthcare }
        \vspace{-1mm}
        \begin{itemize}
            \item Small improvements for severe health conditions \\ \vspace{1mm}
            \tiny(Agha 2014, JHE; McCullough et al 2016, RAND)

@@

            \item Productivity and opinion about EHRs varies drastically \\ \vspace{1mm}
            \tiny (Hitt $\&$ Tambe 2016, ILRR; Butler $\&$ Johnson 2016, IJHEM; Meyerhoefer et al 2016, ILRR)
        \end{itemize}

        \pause

        \column{0.4\textwidth}
        \centering
        \color{blue}
        \underline{ Contribution }
        \vspace{1mm}
        \begin{itemize}
        \color{blue}
            \item No empirical work on EHR/physician effects
            \item Speaks to the puzzling results
            \item Time period 
        \end{itemize}

@@

\begin{frame}{Dep. Variable: Patients Billed with Hospitals}
\begin{figure}[ht]
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_fullsample.pdf}
        \end{minipage}
        \hspace{0.2cm}
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_oldsample.pdf}
        \end{minipage}
    \end{figure}
\end{frame}

@@

\begin{frame}{Plans}
    \begin{itemize}
        \item Analysis on retirement decision of physicians: requires a better understanding of why physicians would drop out of this Medicare data
        \item Endogenous treatment? (Bandwidth, state privacy laws as IV)
        \item Is there substitutability with other types of workers?
    \end{itemize}
\end{frame}
